Debiased calibration for generalized two-Phase sampling

### 2024-04-11 final/reports/prelim_paper_ov.tex
Writing prelim_paper added some of Dr. Kim's comments.

We follow the approach of \cite{kwon2024debiased} for the debiased calibration
method. We consider maximizing the generalized entropy \cite{gneiting2007strictly},

\begin{equation}\label{eq:primalloss}
H(w) = - \sum_{i \in A_2} G(w_i)
\end{equation}

where $G: \mathcal{V} \to \R$ is strictly convex, differentiable function
subject to the constraints:

\begin{equation}\label{eq:calconst1}
\sum_{i \in A_2} \frac{x_i w_i}{\pi_i^{(1)}} = 
\sum_{i \in A_1} \frac{x_i}{\pi_i^{(1)}}
\end{equation}

and

\begin{equation}\label{eq:calconst2}
\sum_{i \in A_2} \frac{g(\pi_{2i|1}^{-1})w_i}{\pi_i^{(1)}} = 
\sum_{i \in A_1} \frac{g(\pi_{2i|1}^{-1})}{\pi_i^{(1)}}.
\end{equation}

The first constraint is the existing calibration constraint and the second
ensures that design consistency is achieved. Here, $g(w) = \partial G / \partial
w$. The original method of \cite{kwon2024debiased} only considered having finite
population quantities on the right hand side of \ref{eq:calconst1}. Let $z_i =
(x_i, g(\pi_{2i|1}^{-1})$. To solve this minimization problem, we use the convex
conjugate function $F(w) = -G(g^{-1}) + g^{-1}(w)w$, and instead find

$$ \hat \lambda = \argmin_{\lambda \in \Lambda_A} \sum_{i \in A_2} F(w_i) +
\lambda_1^T \sum_{i \in A_1} \frac{z_i}{\pi_{2i|1}}$$

for $\Lambda_A = \{\lambda: \lambda^T z_i \in g(\mathcal{V}) \text{ for all } i
\in A_2\}$.

@@

We prove two results in this section is the same spirit as \cite{kwon2024debiased}.
First, we state the assumptions of our analysis then we give the results.

\begin{itemize}
  \item[[A1]] $G(w)$ is strictly convex and twice differentiable in an interval
    $\mathcal{V} \in \R$,
  \item[[A2]] There exists $c_1, c_2 \in \mathcal{V}$ with $c_1, c_2 > 0$ such
    that $c_1 < \pi_{2i|1} < c_2$ for $i = 1, \dots, n$,
  \item[[A3]] If $\pi_{2ij|1}$ is joint inclusion probability of elements $i$
    and $j$ and $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1}\pi_{2j|1}$ then,
    $$\limsup_{n \to \infty} \max_{i,j \in A_1: i \neq j} |\Delta_{2ij|1}| <
    \infty,$$
  % TODO: Check if A4 should be stated for the finite population (as written) or
    % if this should be stated for the Phase 1 sample.
  \item[[A4]] Assume that $\Sigma_z = \lim_{N \to \infty} \sum_{i \in U} z_i
    z_i^T/N$ exists and is positive definite, the average fourth moment of $(y_i,
    x_i^T)$ is finite ($\limsup_{N \to \infty} \sum_{i \in U} ||(y_i, x_i^T)||^4
    / N < \infty$), and $\Gamma(\lambda) = \lim_{N \to \infty}  \sum_{i \in U}
    f'(\lambda^T z_i) z_i z_i^T / N$ exists in a neighborhood around $\lambda_0
    = (\bf 0, 1)$.
  \item[[A5]] FIXME: We need to make an assumption about how Phase 2 relates to
    Phase 1 which relates to the finite population.
\end{itemize}

\begin{theorem}{Design Consistency}
  Suppose that Conditions [A1] - [A5] hold. Then the solution $\hat w$ to 
  \ref{eq:primalloss} subject to \ref{eq:calconst1} and \ref{eq:calconst2} 
  exists and is unique with probability approaching 1. Furthermore, the
  estimator $\hat \theta_{DCE} = \sum_{i \in A_2} \frac{\hat w y_i}{\pi_i^{(1)}}$
  satisfies

  $$\hat \theta_{DCE} = \hat \theta_{DC} + o_p(FIXME)$$

  where $\hat \theta_{DC}$ is the debiased calibration estimator of 
  \cite{kwon2024debiased}.

\end{theorem}

\begin{theorem}(Asymptotic Normality)

\end{theorem}

>>>>

% TODO: Add detailed method for the setup of the debiased calibration method and
% explain how we estimate the weights in two-phase sampling.
% DUE: Thursday April 11

@@
